Quantifying Stability and Change in Personal Culture Using Panel Data

### 2023-09-27 manuscript/manuscript.Rmd
ceiled to capped

```{=latex}
\textit{Notes:} The model estimates the proportion of systematic variance attributable to intrapersonal change. It includes the log of the number of participants, the number of waves the variable was asked (ceiled at t = 10 for each item), the date of the first wave (measured as the year minus 1968 divided by 10), number of waves the question was asked averaged across participants, duration in years per item averaged across participants, and panel and topic fixed effects. Coefficients are estimated from suppressed intercept model based on predictions at participants' wave mid-point. Survey indicators and item topics not shown. See Supplemental Materials B for the full set of coefficients.
\end{figure}
```
\newpage

>>>>

```{=latex}
\textit{Notes:} The model estimates the proportion of systematic variance attributable to intrapersonal change. It includes the log of the number of participants, the number of waves the variable was asked (capped at t = 10 for each item), the date of the first wave (measured as the year minus 1968 divided by 10), number of waves the question was asked averaged across participants, duration in years per item averaged across participants, and panel and topic fixed effects. Coefficients are estimated from suppressed intercept model based on predictions at participants' wave mid-point. Survey indicators and item topics not shown. See Supplemental Materials B for the full set of coefficients.
\end{figure}
```
\newpage
